Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-06-07 manuscript.Rmd
knit!!!1!!one!!

@@

iccs %>% 
  ggplot() +
  geom_col(aes(Group, ICC), fill = "#377eb8") +
  facet_wrap(~model) +
  theme_bw()
```

@@

All analyses were conducted in R’s lme4 package (Bates et al., 2013). The

@@

Since the model for normative thought accuracy is singular, we ran the models separately.

>>>>

Table 2 represents the null models, and Figure 1 represents the ICCs across domains.

@@

iccs %>% 
  ggplot() +
  geom_col(aes(Group, ICC), fill = "#377eb8") +
  labs(title = "Figure 1. ICCs across Domains",
       x = "") +
  facet_wrap(~model) +
  theme_bw()
```

@@

All analyses were conducted in R’s lme4 package (Bates et al., 2013).

@@

Since the model for normative thought accuracy is singular, we ran the models separately. Table 2 represents the normative and distinctive accuracy across domains.
